Multi-Robot Probabilistic Mapping and Exploration

### 2018-07-09 Dissertation/Thesis/tex/intro.tex
updated section 7.4 of dissertation to bring figures together with section 7.3, started defense presentation

The final contribution coordinates the mapping and exploration efforts of multiple robots together. The mapping process is multi-threaded such that multiple members update the same occupancy grid. The exploration algorithm follows a bidding-based structure. Robots compete for tasks in a series of auctions, where the winning bid of one auction affects the bids of subsequent auctions, thereby coordinating the robot efforts. This cooperative approach is computationally-efficient in large environments, and follows a receding-horizon framework, such that map expected information gains are updated as quickly as possible. The proposed coordination is extended to autonomous patrol, where occupancy grid map probabilities are degraded over time, which promotes the robots to revisit areas periodically.

@@

\begin{itemize}
	\item E. Kaufman, K. Takami, T. Lee, and Z. Ai, ``Multi-Vehicle Cooperative Exploration and Patrol of Uncertain 3D Environments'', in preparation.
	\item E. Kaufman and T. Lee, ``Autonomous Aerial Exploration for Topological Mapping of Mars Environments'', \textit{2019 AIAA Guidance, Navigation, and Control Conference}, San Diego, CA, USA, January 2019, submitted.
	\item E. Kaufman, K. Takami, Z. Ai, and T. Lee, ``Autonomous Quadrotor 3D Mapping and Exploration Using Exact Occupancy Probabilities,'' \textit{The Second IEEE International Conference on Robotic Computing}, pp. 49--55, Laguna Hills, January 2018.
	\item E. Kaufman, K. Takami, T. Lee, and Z. Ai, ``Autonomous Exploration with Exact Inverse Sensor Models,'' \textit{Journal of Intelligent }\&\textit{ Robotic Systems}, 2017, doi: 10.1007/s10846-017-0710-7.
	\item E. Kaufman, T. Lee, and Z. Ai, ``Autonomous Exploration by Expected Information Gain from Probabilistic Occupancy Grid Mapping,'' \textit{IEEE International Conference on Simulation, Modeling, and Programming for Autonomous Robots}, pp. 246--251, San Francisco, CA, USA, December 2016.
	\item E. Kaufman, T. Lee, Z. Ai, and I. S. Moskowitz, ``Bayesian Occupancy Grid Mapping via an Exact Inverse Sensor Model,'' \textit{Proceedings of the American Control Conference}, pp. 5709-5715, Boston, MA, USA, July 2016.
	\item E. Kaufman, T. A. Lovell, and T. Lee, ``Nonlinear Observability Measure for Relative Orbit Determination with Angles-Only Measurements,'' \textit{The Journal of the Astronautical Sciences}, 63(1): pp. 60-80, 2016, doi: 10.1007/s40295-015-0082-9.
	\item E. Kaufman, T. A. Lovell, and T. Lee, ``Minimum Uncertainty JPDA Filters and Coalescence Avoidance for Multiple Object Tracking,'' \textit{The Journal of the Astronautical Sciences}, 63(4): pp. 308-334, 2016, doi: 10.1007/s40295-016-0092-2.
	\item T. Wu, E. Kaufman, and T. Lee, ``Globally Asymptotically Stable Attitude Observer on SO(3),'' \textit{Proceedings of the 54th IEEE Conference on Decision and Control}, pp. 2164-2168, Osaka, Japan, December 2015.
	\item E. Kaufman, T. A. Lovell, and T. Lee, ``Nonlinear Observability Measure for Relative Orbit Determination with Angles-Only Measurements,'' \textit{Proceedings of the 25th AAS/AIAA Space Flight Mechanics Meeting}, AAS 15-451, Williamsburg, VA, January 2015.
	\item E. Kaufman, T. A. Lovell, and T. Lee, ``Minimum Uncertainty JPDA Filter and Coalescence Avoidance Performance Evaluations,'' \textit{Proceedings of the 25th AAS/AIAA Space Flight Mechanics Meeting, Williamsburg}, AAS 15-432, VA, January 2015.
	\item E. Kaufman, K. Caldwell, D. Lee, and T. Lee, ``Design and Development of a Free-Floating Hexrotor UAV for 6-DOF Maneuvers,'' \textit{Proceedings of the IEEE Aerospace Conference}, ASC 14-2527, March 2014, Big Sky, MT, USA.
	\item E. Kaufman, T. A. Lovell, and T. Lee, ``Optimal Joint Probabilistic Data Association Filter Avoiding Coalescence in Close Proximity,'' \textit{Proceedings of the European Control Conference}, pp. 2709-2714, Strasbourg, France, June 2014.
	\vspace*{0.5cm}
\end{itemize}

>>>>

\sloppy The final contribution coordinates the mapping and exploration efforts of multiple robots together. The mapping process is multi-threaded such that multiple members update the same occupancy grid. The exploration algorithm follows a bidding-based structure. Robots compete for tasks in a series of auctions, where the winning bid of one auction affects the bids of subsequent auctions, thereby coordinating the robot efforts. This cooperative approach is computationally-efficient in large environments, and follows a receding-horizon framework, such that map expected information gains are updated as quickly as possible. The proposed coordination is extended to autonomous patrol, where occupancy grid map probabilities are degraded over time, which promotes the robots to revisit areas periodically.

@@

\begin{itemize}
	\item E. Kaufman, K. Takami, T. Lee, and Z. Ai, ``Multi-Vehicle Cooperative Exploration and Patrol of Uncertain 3D Environments'', in preparation.
	\item E. Kaufman and T. Lee, ``Autonomous Aerial Exploration for Topological Mapping of Mars Environments'', \textit{2019 AIAA Guidance, Navigation, and Control Conference}, San Diego, CA, January 2019, submitted.
	\item E. Kaufman, K. Takami, Z. Ai, and T. Lee, ``Autonomous Quadrotor 3D Mapping and Exploration Using Exact Occupancy Probabilities,'' \textit{The Second IEEE International Conference on Robotic Computing}, pp. 49--55, Laguna Hills, CA, January 2018.
	\item E. Kaufman, K. Takami, T. Lee, and Z. Ai, ``Autonomous Exploration with Exact Inverse Sensor Models,'' \textit{Journal of Intelligent }\&\textit{ Robotic Systems}, 2017, doi: 10.1007/s10846-017-0710-7.
	\item E. Kaufman, T. Lee, and Z. Ai, ``Autonomous Exploration by Expected Information Gain from Probabilistic Occupancy Grid Mapping,'' \textit{IEEE International Conference on Simulation, Modeling, and Programming for Autonomous Robots}, pp. 246--251, San Francisco, CA, December 2016.
	\item E. Kaufman, T. Lee, Z. Ai, and I. S. Moskowitz, ``Bayesian Occupancy Grid Mapping via an Exact Inverse Sensor Model,'' \textit{Proceedings of the American Control Conference}, pp. 5709-5715, Boston, MA, July 2016.
	\item E. Kaufman, T. A. Lovell, and T. Lee, ``Nonlinear Observability Measure for Relative Orbit Determination with Angles-Only Measurements,'' \textit{The Journal of the Astronautical Sciences}, 63(1): pp. 60-80, 2016, doi: 10.1007/s40295-015-0082-9.
	\item E. Kaufman, T. A. Lovell, and T. Lee, ``Minimum Uncertainty JPDA Filters and Coalescence Avoidance for Multiple Object Tracking,'' \textit{The Journal of the Astronautical Sciences}, 63(4): pp. 308-334, 2016, doi: 10.1007/s40295-016-0092-2.
	\item T. Wu, E. Kaufman, and T. Lee, ``Globally Asymptotically Stable Attitude Observer on SO(3),'' \textit{Proceedings of the 54th IEEE Conference on Decision and Control}, pp. 2164-2168, Osaka, Japan, December 2015.
	\item E. Kaufman, T. A. Lovell, and T. Lee, ``Nonlinear Observability Measure for Relative Orbit Determination with Angles-Only Measurements,'' \textit{Proceedings of the 25th AAS/AIAA Space Flight Mechanics Meeting}, AAS 15-451, Williamsburg, VA, January 2015.
	\item E. Kaufman, T. A. Lovell, and T. Lee, ``Minimum Uncertainty JPDA Filter and Coalescence Avoidance Performance Evaluations,'' \textit{Proceedings of the 25th AAS/AIAA Space Flight Mechanics Meeting, Williamsburg}, AAS 15-432, VA, January 2015.
	\item E. Kaufman, K. Caldwell, D. Lee, and T. Lee, ``Design and Development of a Free-Floating Hexrotor UAV for 6-DOF Maneuvers,'' \textit{Proceedings of the IEEE Aerospace Conference}, ASC 14-2527, March 2014, Big Sky, MT.
	\item E. Kaufman, T. A. Lovell, and T. Lee, ``Optimal Joint Probabilistic Data Association Filter Avoiding Coalescence in Close Proximity,'' \textit{Proceedings of the European Control Conference}, pp. 2709-2714, Strasbourg, June 2014.
	\vspace*{0.5cm}
\end{itemize}

### 2018-07-09 Dissertation/Thesis/tex/multivehicle.tex
updated from tlee edits, more figs for NRL flight experiment
updated section 7.4 of dissertation to bring figures together with section 7.3, started defense presentation

The proposed approach uses auctions and bid modifications based on total map expected information gain and collision-avoidance, promoting exploration of different spaces without explicit consideration of coverage overlaps. The pseudocode for the bidding process is shown with Algorithm \ref{alg:bidding}.

@@

\begin{figure}[!t]
	\centering{
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_1min.jpg}
        		\caption{$1$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_2min.jpg}
        		\caption{$2$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_3min.jpg}
        		\caption{$3$ min}
    	\end{subfigure}
	}
	\centering{
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_4min.jpg}
        		\caption{$4$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_5min.jpg}
        		\caption{$5$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_6min.jpg}
        		\caption{$6$ min}
    	\end{subfigure}
	}
	\centering{
   	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_7min.jpg}
        		\caption{$7$ min}
    	\end{subfigure}
 	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_8min.jpg}
        		\caption{$8$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_9min.jpg}
        		\caption{$9$ min}
    	\end{subfigure}
	}
	\caption{2D Projected Occupancy Grid Map of SEH Second Floor During Multi-Vehicle Exploration}
	\medskip
	\small
	The 2D projected map serves for both entropy and collision information at the exploration height for all three vehicles as they coordinate their mapping efforts with bidding-based multi-vehicle autonomous exploration.
	\label{fig:sim2Dmaps}
\end{figure}

@@

\begin{figure}[!t]
	\centering{
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_1min.jpg}
        		\caption{$1$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_2min.jpg}
        		\caption{$2$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_3min.jpg}
        		\caption{$3$ min}
    	\end{subfigure}
	}
	\centering{
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_5min.jpg}
        		\caption{$5$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_7min.jpg}
        		\caption{$7$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_9min.jpg}
        		\caption{$9$ min}
    	\end{subfigure}
	}
	\centering{
   	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_11min.jpg}
        		\caption{$11$ min}
    	\end{subfigure}
 	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_13min.jpg}
        		\caption{$13$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_15min.jpg}
        		\caption{$15$ min}
    	\end{subfigure}
	}
	\caption{2D Projected Occupancy Grid Map of SEH Second Floor During Multi-Vehicle Patrol}
	\medskip
	\small
	The 2D projected map from of the SEH second floor shows degradation while robots patrol the space. The robots evade the non-cooperative human walking in a rectangular pattern, occasionally capturing the temporarily-occupied space and identifying these cells as occupied on the grid.
	\label{fig:Sim2DMapPatrol}
\end{figure}

>>>>

The proposed approach uses auctions and bid modifications based on total map expected information gain and collision-avoidance, promoting exploration of different spaces without explicit consideration of coverage overlaps. The pseudo-code for the bidding process is shown with Algorithm \ref{alg:bidding}.

@@

\begin{figure}[!t]
	\centering{
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_1min.jpg}
        		\caption{$1$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_2min.jpg}
        		\caption{$2$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_3min.jpg}
        		\caption{$3$ min}
    	\end{subfigure}
	}
	\centering{
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_4min.jpg}
        		\caption{$4$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_5min.jpg}
        		\caption{$5$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_6min.jpg}
        		\caption{$6$ min}
    	\end{subfigure}
	}
	\centering{
   	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_7min.jpg}
        		\caption{$7$ min}
    	\end{subfigure}
 	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_8min.jpg}
        		\caption{$8$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_9min.jpg}
        		\caption{$9$ min}
    	\end{subfigure}
	}
	\caption{2D Projected Occupancy Grid Map During Multi-Vehicle Exploration}
	\medskip
	\small
	The 2D projected map serves for both entropy and collision information at the exploration height for all three vehicles as they coordinate their mapping efforts with bidding-based multi-vehicle autonomous exploration.
	\label{fig:sim2Dmaps}
\end{figure}

@@

\begin{figure}[!t]
	\centering{
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_1min.jpg}
        		\caption{$1$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_2min.jpg}
        		\caption{$2$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_3min.jpg}
        		\caption{$3$ min}
    	\end{subfigure}
	}
	\centering{
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_5min.jpg}
        		\caption{$5$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_7min.jpg}
        		\caption{$7$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_9min.jpg}
        		\caption{$9$ min}
    	\end{subfigure}
	}
	\centering{
   	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_11min.jpg}
        		\caption{$11$ min}
    	\end{subfigure}
 	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_13min.jpg}
        		\caption{$13$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_15min.jpg}
        		\caption{$15$ min}
    	\end{subfigure}
	}
	\caption{2D Projected Occupancy Grid Map During Multi-Vehicle Patrol}
	\medskip
	\small
	The 2D projected map from of the SEH second floor shows degradation while robots patrol the space. The robots evade the non-cooperative human walking in a rectangular pattern, occasionally capturing the temporarily-occupied space and identifying these cells as occupied on the grid.
	\label{fig:Sim2DMapPatrol}
\end{figure}

### 2018-07-09 Dissertation/Thesis/tex/results.tex
updated section 7.4 of dissertation to bring figures together with section 7.3, started defense presentation

@@

Several components are used for localization, sensing, and actuation. A Vicon motion capture system provides the transformation between a reference frame fixed to the world and the moving vehicle. This transformation, along with fixed transformations between the robot body and the sensors, provides sufficient information for the transformation from the world to each sensor frame. The sensor readings from the Xtion and Hokuyo are transmitted from an NVidia Jetson TX2 onboard the vehicle (Figure \ref{fig:QuadrotorHardware}). The sensor readings are received via WIFI on a host computer with an Intel Core i7-6800K CPU (12$\times$3.40GHz), which runs the mapping and exploration nodes. The host computer returns the exploration trajectories to the Jetson TX2 over WIFI. Then, the Jetson executes a nonlinear geometric flight controller~\cite{GooDaeLee13} onboard. With this configuration, large processing tasks are avoided onboard the robot.

@@

\section{Full 3D Exploration with a Quadrotor}
\label{sec:QuadrotorSEH}

In this final experiment, we introduce the quadrotor to a space with complex 3D objects. The robot generates a 3D map of this space, and performs autonomous exploration while considering the expected information gains of sample measurement rays with nonzero vertical components. The robot unlike prior examples, the robot also moves vertically during exploration and tracks the ground below the vehicle.

\subsection{3D Exploration Setup and Parameters}
The software follows the same structure as in Section \ref{sec:MarsSimulation}, except the Gazebo simulated environment is replaces with experimental equipment. This equipment is identical to the prior experimental example (Section \ref{sec:QuadrotorNRL}), except the experiment took place at the Flight Dynamics and Control Lab (FDCL) inside the second floor of SEH. This environment is smaller with only $6$ cameras, where the x-direction (positive east) spans $-2.0$ m to $2.0$ m, the y-direction (positive north) spans $-2.0$ m to $2.0$ m, and the z-direction (positive vertically up) spans $-0.15$ m to $1.5$ m.

@@

@@

@@

\begin{figure}[!t]
\centering
    	\begin{subfigure}[t]{0.8\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{connected_costmap.png}
        		\caption{Connected Cost Map Cross-Section}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.8\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{disconnected_costmap.png}
        		\caption{Disconnected Cost Map Cross-Section}
    	\end{subfigure}
	\caption{2D Cross-Sections of 3D Cost Maps}
	\medskip
	\small
	Two examples of the 3D cost maps from Dijkstra's search show connected and disconnected regions at the exploration height, where more blue regions have small distance costs, red regions have larger distance costs, and pink regions are unreachable due to collision risk. In (a), the robot does not have to change altitude to reach any of the collision-free poses. However in (b), the robot can only reach collision-free poses in the disconnected section by changing altitude.
	\label{fig:Full3DExplorationCostmaps}
\end{figure}

>>>>

\section{Geometric Control}
\label{sec:GeometricControl}

The next two experiments involve a quadrotor unmanned aerial vehicle (UAV) mapping and exploring 3D environments. A flight controller that accounts for the nonlinear quadrotor attitude dynamics is required to track the trajectories provided by autonomous exploration. We choose geometric control because of its stability properties and simple form.

Geometric control is designed for rigid-body attitude dynamics, and is developed directly on $\SO$ without local parameterizations such as Euler angles or quaternions. Therefore, this approach avoids singularities, ambiguities, and linearization errors. It has been developed for fully-actuated vehicles~\cite{KauCalLeeLee14} and for under-actuated quadrotors~\cite{LeeLeoMcc10,LeeLeo_4457,LeeLeo,GooDaeLee13}. This approach is further extended to aerial load transportation~\cite{GooLee14,GooLee16} and attitude estimation~\cite{WuKauLee15}.

In the context of quadrotor control, the main idea is that a translational position-integral-derivative (PID) control produces a desired force in 3D, and the robot selects a desired attitude $R_d$ and angular velocity $\Omega_d$ to align its propellers with this force and to correct its first body-fixed axis to a desired direction. The attitude and angular velocity errors from the current robot attitude $R$ and angular velocity $\Omega$ are 
\begin{align}
e_R&=(R_d^\T R-R^\T R_d)^{\mathsf{V}},
\\
e_\Omega&=\Omega-R^\T R_d\Omega_d,
\end{align}
respectively, where the \emph{vee} map is defined in~\cite{LeeLeo}. The quadrotor is capable of producing a force $f\in\Re$ and moment $M\in\Re^3$,
\begin{align}
\label{eqn:geometricf}
f&=(k_xe_x+k_ve_v+mge_3-m\ddot{x}_d)\cdot Re_3,
\\
\label{eqn:geometricM}
M&=-k_Re_R-k_\Omega e_\Omega+\Omega\times J\Omega-J(\hat{\Omega}R^\T R_d\Omega_d-R^\T R_d\dot\Omega_d),
\end{align}
where $e_x$ and $e_v$ are position and velocity errors, respectively, $k_x$, $k_v$, $k_R$, $k_\Omega$ are positive gain constants, $\ddot{x}_d$ is the desired translational acceleration, $\dot{\Omega}_d$ is the desired rotational acceleration, $m$ is the quadrotor mass, $J$ is the quadrotor moment of inertia, $e_3=[0, 0, 1]^\T$, and the \emph{hat} map is defined in~\cite{LeeLeo}. Since \refeqn{geometricf} and \refeqn{geometricM} require only trivial calculations, they are easily computed with onboard modules.

@@

Several components are used for localization, sensing, and actuation. A Vicon motion capture system provides the transformation between a reference frame fixed to the world and the moving vehicle. This transformation, along with fixed transformations between the robot body and the sensors, provides sufficient information for the transformation from the world to each sensor frame. The sensor readings from the Xtion and Hokuyo are transmitted from an NVidia Jetson TX2 onboard the vehicle (Figure \ref{fig:QuadrotorHardware}). The sensor readings are received via WIFI on a host computer with an Intel Core i7-6800K CPU (12$\times$3.40GHz), which runs the mapping and exploration nodes. The host computer returns the exploration trajectories to the Jetson TX2 over WIFI. Then, the Jetson executes the geometric flight controller onboard. With this configuration, large processing tasks are avoided onboard the robot.

@@

%\newpage

%\let\oldsection\section
%\renewcommand\section{\clearpage\oldsection}

\sectionbreak{\clearpage}
\section{Full 3D Exploration with a Quadrotor}
\label{sec:QuadrotorSEH}

In this final experiment, we introduce the quadrotor to a space with complex 3D objects. The robot generates a 3D map of this space, and performs autonomous exploration while considering the expected information gains of sample measurement rays with nonzero vertical components. Unlike prior examples, the robot also moves vertically during exploration and tracks the ground below the vehicle.

\subsection{3D Exploration Setup and Parameters}
The software follows the same structure as in Section \ref{sec:MarsSimulation}, except the Gazebo simulated environment is replaced with experimental equipment. This equipment is identical to the prior experimental example (Section \ref{sec:QuadrotorNRL}), except the experiment takes place at the Flight Dynamics and Control Lab (FDCL) inside the second floor of SEH, and the Hokuyo is no longer in use. This environment is smaller with only $6$ cameras, where the x-direction (positive east) spans $-4.5$ m to $4.5$ m, the y-direction (positive north) spans $-4.0$ m to $4.5$ m, and the z-direction (positive vertically up) spans $-0.25$ m to $2.0$ m, shown in Figure \ref{fig:Full3DExplorationEnvironment}.

@@

The experimental results show that the robot successfully explores a 3D space, capturing occupied space above and below the robot. The quadrotor does an initial rotation over $20$ sec, then explores the space with planned motions in all three dimensions, shown in Figure \ref{fig:exp3DVid}. The robot generates a 3D probabilistic map (Figure \ref{fig:exp3DOccMap}) and uses this for entropy prediction and collision-free motion planning with a 3D cost map (Figure \ref{fig:Full3DExplorationCostmaps}).

@@

\begin{figure}[!t]
\centering
    	\begin{subfigure}[t]{0.8\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{connected_costmap.png}
        		\caption{Connected Cost Map Cross-Section}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.8\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{disconnected_costmap.png}
        		\caption{Disconnected Cost Map Cross-Section}
    	\end{subfigure}
	\caption{2D Cross-Sections of 3D Cost Maps}
	\medskip
	\small
	Two examples of the 3D cost maps from Dijkstra's search show connected and disconnected regions at the exploration height, where more blue regions have smaller distance costs, red regions have larger distance costs, and pink regions are unreachable due to collision risk. In (a), the robot does not have to change altitude to reach any of the collision-free poses at its current altitude. However in (b), the robot can only reach collision-free poses in the disconnected section by changing altitude and following the 3D cost map.
	\label{fig:Full3DExplorationCostmaps}
\end{figure}

The proposed 3D occupancy grid mapping and autonomous exploration approaches complement each other well. The floor and objects are well-captured, as this detail-oriented entropy-based exploration scheme tends to generate completely mapped regions before moving to new terrain, shown with Case 1 of the Mars exploration numerical example (Section \ref{sec:MarsSimulation}). As a result, the entropy decreases fairly steadily over the experiment, shown in Figure \ref{fig:Explore3D_H}.

A key improvement to prior experiments is the ability to consider the occupancy properties in full 3D. This allows the robot to understand that the mannequin occupies some space that the robot must avoid. However, the robot also recognizes that the space above the mannequin is free, and it chooses a trajectory above the mannequin to reach new terrain. At other times, the robot observes spaces from lower vantage points, which can be advantageous with a short sensor range and the forward direction of the Asus Xtion. These added capabilities are attributed to the full 3D mapping and exploration approach.

@@
